---
title: "Create tables"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Create tables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  eval = TRUE,
  fig.align = "center"
)
```

First, open `AKesp.Rproj` and run:
```{r}
devtools::load_all()
```

Eventually the package will be on Github!

Most tables are automatically created from the `table_spreadsheet.csv` and the `.csv` files in the `tables` folder. However, the `AKesp` package can also create some tables that require data analysis. 

## Traffic light scores

A traffic light table can be automatically created from a spreadsheet that has a column for year and a column for each indicator.
```{r}
AKesp::esp_traffic_tab(data = AKesp::sablefish, 
                       year = 2020)
```

Multiple years can be shown.
```{r}
AKesp::esp_traffic_tab(data = AKesp::sablefish, 
                       year = 2016:2020)
```
