

# Current Year Update {-}

The ecosystem and socioeconomic profile or ESP is a standardized framework for compiling and evaluating relevant stock-specific ecosystem and socioeconomic indicators and communicating linkages and potential drivers of the stock within the stock assessment process (Shotwell et al., In Review). The ESP process creates a traceable pathway from the initial development of indicators to management advice and serves as an on-ramp for developing ecosystem-linked stock assessments. 
Please refer to the last full ESP and partial ESP documents for further information regarding the ecosystem and socioeconomic linkages for this stock (*list references*).

## Management Considerations {-}

Summary conclusions from ESP for ABC (risk table) 

## Modeling Considerations {-}

Summary of indicators with high importance in the Bayesian adaptive sampling routine and discussion of which indicators have had consistent high importance. 
List of research ecosystem model runs that are currently ongoing and potential for operational use in the future. 

# Assessment {-}

## Ecosystem and Socioeconomic Processes {-}

One paragraph description of ecosystem and socioeconomic (if available) conceptual model(s)

## Indicator Suite {-}

One paragraph description of LME level indicators relevant to stock (ESR summary)

### Ecosystem Indicators: {-}
```{r, eco_ind, message = TRUE} 
eco <- AKesp::list_indicators(data = esp_data, # must be defined in parent doc
                              indicator_type = "Ecosystem") %>%
  try()
# not sure why, but this is creating a double vector with exactly the same info in each element
# cutting to just the first element bc I can't figure out why this is happening
# does not happen w socioeco data
cat(eco[1], sep = "\n\n")
```

### Socioeconomic Indicators: {-}

```{r, socio_ind, message = TRUE}
socio <- AKesp::list_indicators(data = esp_data, # must be defined in parent doc 
                                indicator_type = "Socioeconomic") %>%
  try()
cat(socio, sep = "\n\n")
```

## Indicator Monitoring Analysis {-}

References for statistical tests for monitoring indicator suite by stage where relevant 

### Beginning Stage: Traffic Light Test {-}

One paragraph summary of indicator status and trends over time and last five years trend
Report scores by category (if applicable) and overall ecosystem and socioeconomic indicators. 

### Intermediate Stage: Importance Test {-}

One paragraph summary of importance results with analysis of highly explanatory variables for stock assessment input of interest (e.g., recruitment estimates)

### Advanced Stage: Research Model Test {-}

Update on ecosystem linked model in development and link to relevant literature or report on model 

# Data Gaps and Future Research Priorities {-}

Copy from full ESP
