---
title: "Appendix `r params$num`. Ecosystem and Socioeconomic Profile of the `r params$fish` stock in the `r params$region` `r ifelse(params$esp_type == 'report_card', '- Report Card', ifelse(params$esp_type == 'partial', '- Partial Update', ''))`"
author: "`r params$authors`"
date: "Draft `r params$year`"
output: 
  bookdown::word_document2:
    reference_docx: "template.docx"
    fig_caption: false
    
bibliography: references.bib

params:
  num: 1
  authors: "Kalei Shotwell, Abby Tyrell"
  year: 2022
  contributors: "Kalei Shotwell, Abby Tyrell"
  fish: "Myfish"
  region: "Myarea"
  region_abbreviation: "Myabbrev"
  fig_spreadsheet: 
  tab_spreadsheet: 
  esp_text: 
  stock_image: "default"
  esp_data: NULL
  con_model_path: "default"
  bayes_path: "default"
  ncolumn: 1
  min_year: NULL
  working_dir:
  esp_type: "full"
---

```{r setup, include = FALSE}
# This template can be used to create a full or partial ESP
# The text content is read in from a word document
# The word document should be created based on the template
# Headings and table/figure references must follow specific formatting

# message((params$esp_data))

esp_data <- eval(params$esp_data)

# message(head(esp_data))

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  results = "asis"
)

fig_spreadsheet <- params$fig_spreadsheet
tab_spreadsheet <- params$tab_spreadsheet
ref_spreadsheet <- params$ref_spreadsheet
esp_text <- params$esp_text
con_model_path <- params$con_model_path
bayes_path <- params$bayes_path
stock_image <- params$stock_image

if (stock_image == "default") {
  stock_image <- system.file("images/noaa.jpg", package = "AKesp")
}

if (con_model_path == "default") {
  con_model_path <- system.file("images/noaa.jpg", package = "AKesp")
}

if (bayes_path == "default") {
  bayes_path <- system.file("images/noaa.jpg", package = "AKesp")
}
```

```{r, title-fig}
knitr::include_graphics(path = stock_image,
                        rel_path = FALSE)
```

*With Contributions from:*

`r params$contributors`

\newpage

```{r, text-report-card, eval = params$esp_type == "report_card"}
child <- knitr::knit_child(system.file("esp-report-card-child.Rmd", package = "AKesp"),
  quiet = TRUE
)
cat(child, sep = "\n\n")
```

```{r, text, eval = params$esp_type != "report_card"}
if (class(try(readtext::readtext(esp_text)))[1] == "try-error") {
  print("Can't find text template!")
} else {
  temp_file <- "temp-text.txt"
  invisible(file.create(temp_file))

  text <- readtext::readtext(file = esp_text)
  writeLines(text = text$text, con = temp_file)

  new_text <- readLines(temp_file)
  # remove instructions section
  new_text <- new_text[stringr::str_which(new_text, "# Executive Summary"):length(new_text)]

  # knit to new .txt
  knit_Rmd <- ("temp-text-knit.txt")
  invisible(file.create(knit_Rmd))

  knitr::knit(
    text = new_text,
    output = knit_Rmd,
    quiet = TRUE
  )

  # include knitted text
  cat(readLines(knit_Rmd), sep = "\n\n")

  # clean up temp files
  invisible(file.remove(temp_file, knit_Rmd))
}
```

\newpage

# Tables {-}

```{r, standard-tables, message = FALSE, include = params$esp_type == "report_card"}
child <- knitr::knit_child(system.file("table-child.Rmd", package = "AKesp"),
  quiet = TRUE)
cat(child, sep = "\n\n")
```

```{r, tables, message = FALSE, eval = params$esp_type != "report_card"}
# otherwise, make tables according to spreadsheet
if (class(try(read.csv(file = tab_spreadsheet)))[1] != "try-error") {
  
  # read spreadsheet
  tabs <- read.csv(file = tab_spreadsheet)
  # print(tabs)

for (i in 1:nrow(tabs)) {
  cat("\n\n")

  if (tabs$chunk_name[i] == "eco-table") {
  child <- knitr::knit_child(text = "```{r, label = new-eco-table, ref.label = c('table-set-up', 'eco-table')}
                             ```",
                             quiet = TRUE)
  cat(child, sep = "\n\n")

  } else if (tabs$chunk_name[i] == "socio-table") {
  child <- knitr::knit_child(text = "```{r, label = new-socio-table, ref.label = c('table-set-up', 'socio-table')}
                             ```",
                             quiet = TRUE)
  cat(child, sep = "\n\n")

  } else {
    tab <- tabs$file_name[i]
    # print(tab)
    AKesp::render_tab(
      lab = tabs$chunk_name[i],
      cap = tabs$caption[i]
    ) %>%
      try()
  }

  cat("\n\n")
}
} else {
  message("You are not creating a report card, and the table spreadsheet is missing!")
}
```

\newpage

# Figures {-}

```{r, standard-figures, fig.height = 8, include = params$esp_type == "report_card"}
child <- knitr::knit_child(system.file("figure-child.Rmd", package = "AKesp"),
    quiet = TRUE)
cat(child, sep = "\n\n")
```

```{r, figures, eval = params$esp_type != "report_card"}
# a report card automatically pulls in (from paths specified in .Rmd params):
# fig 1: conceptual model
# fig 2: ecosystem traffic light figs
# fig 3: socioeconomic traffic light figs
# fig 4: overall traffic score summary
# fig 5: bayesian summary

# otherwise, all figures need to be specified

if (class(try(read.csv(file = fig_spreadsheet)))[1] != "try-error") {
  
  figs <- read.csv(file = fig_spreadsheet)

  for (i in 1:nrow(figs)) {
    if (figs$chunk_name[i] == "conceptual-model") {

       child <- knitr::knit_child(text = "```{r, conceptual-model, fig.height = 8}
                                ```",
                                quiet = TRUE)
       cat(child, sep = "\n\n")
    
} else if (figs$chunk_name[i] == "traffic-eco") {
       child <- knitr::knit_child(text = "```{r, traffic-eco-setup}
                                ```",
                                quiet = TRUE)
       cat(child, sep = "\n\n")
       
       child <- knitr::knit_child(text = "```{r, traffic-eco, fig.height = 7, fig.width = 6, fig.keep = 1}
                                ```",
                                quiet = TRUE)
       cat(child, sep = "\n\n")

    } else if (figs$chunk_name[i] == "traffic-socio") {
             child <- knitr::knit_child(text = "```{r, traffic-socio-setup, fig.cap = 'dummy caption'}
                                ```",
                                quiet = TRUE)
             cat(child, sep = "\n\n")

       child <- knitr::knit_child(text = "```{r, traffic-socio, fig.height = 7, fig.width = 6, fig.keep = 1}
                                ```",
                                quiet = TRUE)
       cat(child, sep = "\n\n")

    } else if (figs$chunk_name[i] == "overall") {
       child <- knitr::knit_child(text = "```{r, overall, fig.height = 7}
                                ```",
                                quiet = TRUE)
       cat(child, sep = "\n\n")

    } else if (figs$chunk_name[i] == "bayesian") {
       child <- knitr::knit_child(text = "```{r, bayesian, fig.height = 8}
                                ```",
                                quiet = TRUE)
       cat(child, sep = "\n\n")

    } else {
      # pat <- here::here(params$working_dir, )
      # print(pat)
      try(AKesp::render_fig(
        img = figs$file_name[i],
        lab = figs$chunk_name[i],
        cap = figs$caption[i],
        alt = figs$alt_text[i]
      ))
    }
  }
  
  if("traffic-eco" %in% figs$chunk_name) {
    
           child <- knitr::knit_child(text = "## Full ecosystem traffic figures
           Manually move these to their proper location above
           ```{r, traffic-eco-setup}
                                ```",
                                quiet = TRUE)
       cat(child, sep = "\n\n")
       
       child <- knitr::knit_child(text = "```{r, traffic-eco, fig.height = 7, fig.width = 6}
                                ```",
                                quiet = TRUE)
       cat(child, sep = "\n\n")
  }
  
  if("traffic-socio" %in% figs$chunk_name) {
       
       child <- knitr::knit_child(text = "## Full socioeconomic traffic figures
           Manually move these to their proper location above
           ```{r, traffic-socio-setup}
                                ```",
                                quiet = TRUE)
       cat(child, sep = "\n\n")

       child <- knitr::knit_child(text = "```{r, traffic-socio, fig.height = 7, fig.width = 6}
                                ```",
                                quiet = TRUE)
       cat(child, sep = "\n\n")
    
  }
  
} else {
  message("You are not creating a report card, and the figure spreadsheet is missing!")
}
```
